Light inextensible strings under tension in the Schwarzschild geometry

### 2018-10-03 string_microarticle.tex
minor wordsmithing to the abstract

\begin{abstract}
%%%
Here I analyze the behaviour of stationary, light inextensible strings
under tension in the vicinity of a nonrotating black hole.  Such
strings minimize their proper length, given by integrating the spatial
equatorial component of the Schwarzshild metric.  The string path is
calculated by numerical solution to the Euler-Lagrange equations.  If
the string is entirely outside the event horizon, its closest approach
is to the singularity is tangential; if the distance of closest
approach is less than about $1.076109317\cdot(2GM)$, the string
self-intersects.  Light taut strings interpret the concept ``straight
line'' and their behaviour suggests a possible way of manipulating a
black hole.
%%%%
\end{abstract}

>>>>

\begin{abstract}
%%%
Here I analyze the behaviour of stationary, light inextensible strings
under tension in the vicinity of a nonrotating black hole.  Such
strings minimize their proper length, given by integrating the spatial
component of the Schwarzshild metric along the string.  The path is
calculated by numerical solution to the Euler-Lagrange equations.  If
the string is entirely outside the event horizon, its closest approach
is to the singularity is tangential; if the distance of closest
approach is less than about $1.076109317$ Schwarzschild radii, the
string self-intersects.  If the string attains $r=2GM$, then it will
in general be tangential to the event horizon at that point.  Light
taut strings interpret the concept ``straight line'' and their
behaviour suggests a possible way of manipulating a black hole.
%%%%
\end{abstract}
